Figures

### 2020-01-17 figures/00_maps.Rmd
add map of depth availability in limno lakes

# add text labels of proportions

>>>>

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  geom_sf_text(data = dt_plot, 
               aes(label = round(prop_maxdepth, 2)), 
               size = 2.5) +
  labs(fill = "") +
  coord_sf(datum = NA) + theme_void()

# limit to lakes with limno data
dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  dplyr::filter(has_limno == 1) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth))
st_geometry(dt_plot) <- dt_plot$geom

### 2020-01-17 manuscript/figures.Rmd
add map of depth availability in limno lakes

```{r maps_state, fig.cap = "Proportion of lakes greater than 4ha with maximum depth availability by state.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_state-1.pdf")
```

>>>>

```{r maps_state_all, fig.cap = "Proportion of ALL lakes greater than 4ha with maximum depth availability by state.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_state-1.pdf")
```

```{r maps_state_limno, fig.cap = "Proportion of lakes with limno data greater than 4ha with maximum depth availability by state.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_state-2.pdf")
```
